Learning to Synthesize Rules for Rule-based Intrusion Detectors

### 2020-03-06 paper/paper.tex
snapshot

\newcommand{\numNonContentAttacks}{5}
\newcommand{\numContentAttacks}{10}

@@

\vspace{1ex}
\subsubsection{Attacks.}~Table~\ref{table:attacks} shows the selection
of attacks we analyzed.  Non-http attacks are listed at the top of the
table whereas http attacks are listed at the bottom. Recall from
Section~\ref{sec:reverse-engineering} that (1) http attacks are
prevalent, (2) most http attacks use only content options, and (3)
most non-http attacks only use field options. We selected from various
sources \numNonContentAttacks\ non-http attacks and
\numContentAttacks\ http attacks. The higher number of http attacks
reflects their popularity. Column ``Name'' shows the name of the
attack, column ``Source'' shows the source where we obtained data to
reproduce the attack (see Section~\ref{subsec:malicious-traffic}),
column ``Type'' shows the kind of attack, column ``Protocol'' shows
the name of the protocol explored in the attack, and column ``Ground
Truth'' shows the rule options to capture the attack. The rationale
for the selection were (1) to cover various kinds of attacks and (2)
to cover attacks of various protocols. Considering (1), the selection
includes attacks of the following types: Denial-of-Service
(DoS)~\cite{denial-of-service}, Active Reconnaissance
(AREC)~\cite{active-reconnaissance}, Privilege escalation
(PESC)~\cite{privilege-escalation}, Remote Code Execution
(RCE)~\cite{remote-code-execution}, Local File Inclusion
(LFI)~\cite{local-file-inclusion}, and Policy Violation
(PVE)~\Fix{local-file-inclusion}.

@@

To answer this research question, we selected two cases with the
highest number of examples (see column ``\#~Vars'' on
Table~\ref{table:results})---idqaccess and scripttag---and the case
where \tname\ performs worst---jboss. We measured the position of the
golden rule at the rank for an increasing number of of examples
provided to \tname. For each number of variants, we sampled five sets
of that size to provide as input to the
technique. Figure~\ref{fig:impact-number-attacks} shows the results
for each attack we selected. The y-axis of each plot denotes the rank
of the golden rule and x-axis denotes the number of attack examples
used to synthesize rules. Each point in the x-axis is associated with
a boxplot for the distribution of results for the corresponding number
of variants. Note that 1) the number of examples is important, 2) the
choice of examples is important, and 3) a small number of examples
suffices to reach the best results.

@@

\Mar{coloquem os numeros aqui para que eu gere o boxplot amanha,
  depois da aula.

  *** posicao no ranking (numeros artificais. por favor, substituam) ***

  ataque 1:

    1 variacao:  10, 20, 4, 2, 5

    5 variacoes: 5, 4, 4, 2, 3

    10 variacoes: 1, 2, 1, 2, 1

    (ate numero de variacoes que aparece na Tabela 3)

  ataque 2:
     ...

@@

External Validity. \Fix{elaborate ...how popular are
  Suricata/Metasploit?}

>>>>

\newcommand{\numNonContentAttacks}{4}
\newcommand{\numContentAttacks}{10}

@@

\vspace{1ex}
\subsubsection{Attacks.}~Table~\ref{table:attacks} shows the selection
of attacks we analyzed.  Non-http attacks are listed at the top of the
table and http attacks are listed at the bottom. Recall from
Section~\ref{sec:reverse-engineering} that (1) http attacks are
prevalent, (2) most http attacks use only content options, and (3)
most non-http attacks only use field options. We selected
\numNonContentAttacks\ non-http attacks and \numContentAttacks\ http
attacks. The higher number of http attacks reflects their
popularity. Column ``Name'' shows the name of the attack, column
``Source'' shows the source where we obtained data to reproduce the
attack (see Section~\ref{subsec:malicious-traffic}), column ``Type''
shows the kind of attack, column ``Protocol'' shows the name of the
protocol explored in the attack, and column ``Ground Truth'' shows the
rule options to capture the attack. The rationale for the selection
were (1) to cover various kinds of attacks and (2) to cover attacks of
various protocols. Considering (1), the selection includes attacks of
the following types: Denial-of-Service (DoS)~\cite{denial-of-service},
Active Reconnaissance (AREC)~\cite{active-reconnaissance}, Privilege
escalation (PESC)~\cite{privilege-escalation}, Remote Code Execution
(RCE)~\cite{remote-code-execution}, and Local File Inclusion
(LFI)~\cite{local-file-inclusion}.

%, and Policy Violation (PVE).

@@

To answer this research question, we selected two cases with the
highest number of examples (see column ``\#~Vars'' on
Table~\ref{table:results})---idqaccess and scripttag---and the case
where \tname\ performs worst---jboss. We measured the position of the
golden rule at the rank for an increasing number of of examples
provided to \tname. For each number of variants, we sampled five sets
of that size to provide as input to the
technique. Figure~\ref{fig:impact-number-attacks} shows the results
for each attack we selected. The y-axis of each plot denotes the rank
of the golden rule and x-axis denotes the number of attack examples
used to synthesize rules. Each point in the x-axis is associated with
the boxplot of the distribution of results for the corresponding
number of variants.

@@

Results indicate that 1) the number of examples is important, 2) the
choice of examples is important, and 3) a small number of examples
suffices to reach the best results.

\begin{center}
\begin{tcolorbox}[enhanced,width=3.3in,center upper,drop shadow southwest,sharp corners]
As expected, \tname\ is sensitive to the number and choice of example
input attacks. However, a small number of examples suffices to achieve
best results.
\end{tcolorbox}
\end{center}

@@

Our experiments is affected by the usual threats. Considering external
validity. Our results cannot be generalized beyond the subjects we
selected. To mitigate that threat we selected a variety of attacks
with different characteristics. Considering internal validity, the
implementation of \tname\ could contain errors. We mitigated that
threat by carefully inspecting code and results. Considering construct
validity, the choice of metric used to evaluate the approach may not
be applicable in practice. We considering the use of ranking of the
golden rule a reasonable choice as the approach places the golden rule
close to the top in most cases.
